
Todos until deadline: tags: (in progress) (finished) (not started)

major todos:

1. in progress: 

read through and cite references: 
    J. McAuley, J. Leskovec, and D. Jurafsky. Learning attitudes and attributes from multi-aspect reviews. ICDM, 2012.
    J. McAuley and J. Leskovec. From amateurs to connoisseurs: modeling the evolution of user expertise through online reviews. WWW, 2013.

2. in progress: research similar papers within multi-aspect NLP and sentiment domain 

3. Michi, not started: include references to latex document

4. Question: I would prefer including an Abstract/ executive summary





minor todos:

0. not started: if we follow current introduction: include statistics about beer consumption

3. not started: find papers about the but-multiplier




Outlook: 
- Special attention can be devoted to sentiment-sensitive information like punctuation, smileys and capitalization.
- extend wordlist for each aspect
- was machen wir jetzt eigtl mit wörtern wie palate, taste etc. also unsere filter words? lassen wirs so?
- holdout dataset to account for risk of overfitting
- learn user rating behavior, acknowledge for individual differences in average score
- For each aspect we could separately model the words that discuss an aspect and words that discuss sentiment about an aspect.




References:

@misc{nakatani2010langdetect,
  title  = {Language Detection Library for Java},
  author = {Shuyo, Nakatani},
  url    = {http://code.google.com/p/language-detection/},
  year   = {2010}
}


Kristina Toutanova and Christopher D. Manning. 2000. Enriching the Knowledge Sources Used in a Maximum Entropy Part-of-Speech Tagger. In Proceedings of the Joint SIGDAT Conference on Empirical Methods in Natural Language Processing and Very Large Corpora (EMNLP/VLC-2000), pp. 63-70.


Kristina Toutanova, Dan Klein, Christopher Manning, and Yoram Singer. 2003. Feature-Rich Part-of-Speech Tagging with a Cyclic Dependency Network. In Proceedings of HLT-NAACL 2003, pp. 252-259.






